factor_explorer

### 2014-06-22 ijlyttle/factor_explorer.Rmd
new version of explorer

# 2014-06-20
# for what it's worth, I'm running the latest versions of RStudio (0.98.932 )and 
# github versions of "rstudio/shiny", "rstudio/rmarkdown", "yihui/knitr"
```

@@

var_names_student_subject <- 
  var_names_student[c(
    seq(501, 505), # math
    seq(541, 545), # reading
    seq(546, 551)  # science
  )]

@@

rct_count <- reactive({
  df <-
    rct_data() %>%
    group_by()
})

@@

renderPlot({
  ggplot(
    data = rct_data()
  ) + 
  geom_violin(
    aes_string(
      x = input$x_factor, 
      y = input$subject),
      scale = "width"
  ) + 
  geom_boxplot(
    aes_string(
      x = input$x_factor,
      y = input$subject,
      fill = input$fill_factor
    )  
  ) + 
  facet_grid(CNT ~ .) + 
  scale_x_discrete(name = rct_labels()[["x"]]) +  
  scale_y_continuous(limits = c(0, 1000), name = rct_labels()[["y"]]) +
  scale_fill_discrete(name = rct_labels()[["fill"]]) 
})
```

>>>>

# 2014-06-20
# for what it's worth, I'm running the latest versions of RStudio (0.98.932 )and 
# github versions of "rstudio/shiny", "rstudio/rmarkdown", "yihui/knitr", "hadley/tidyr"
```

@@

var_names_student_subject <- 
  var_names_student[c(
    seq(501, 505), # math
    seq(541, 545), # reading
    seq(546, 550)  # science
  )]

@@

rct_count <- reactive({

  # hacky hacky hacky  
  str_symbols <- c("CNT", input$x_factor, input$fill_factor) 
  symbols <- str_symbols %>% lapply(as.symbol)

  df_data <- rct_data()

  if (nrow(df_data) == 0)
    return(NULL)

#   # get counts by category
   df <- 
     df_data[, str_symbols] %>%
     regroup(symbols) %>%
     summarize(n = n())

  # get counts by country  
  df_cnt <-
    rct_data() %>%
    group_by(CNT) %>%
    summarize(n_country = n(), y_placeholder = 0)

  # join, get proportion by country for each category
  df_new <- 
    left_join(df, df_cnt, by = "CNT") %>%
    mutate(prop = n / n_country)

  df_new
})

observe({  
  print(rct_count())
  print("")
#  print(str(rct_count()))
#  print("")
#  print(summary(rct_count()))
})

@@

renderPlot({
  ggplot(
    data = rct_data()
  ) + 
  geom_violin(
    aes_string(
      x = input$x_factor, 
      y = input$subject),
      scale = "width"
  ) + 
  geom_boxplot(
    aes_string(
      x = input$x_factor,
      y = input$subject,
      fill = input$fill_factor
    ),
    alpha = 0.75
  ) + 
#   geom_dotplot(
#     aes_string(
#       x = input$x_factor,
#       y = input$subject,
#       fill = input$fill_factor
#     ),
#     binaxis = "y", 
#     stackdir = "center", 
#     position = "dodge") + 
  facet_grid(CNT ~ .) + 
  scale_x_discrete(name = rct_labels()[["x"]]) +  
  scale_y_continuous(limits = c(0, 1000), name = rct_labels()[["y"]]) +
  scale_fill_brewer(type = "seq", name = rct_labels()[["fill"]]) 
})

renderPlot({
  ggplot(
    aes_string(
      x = input$x_factor,
      fill = input$fill_factor
    ),
    data = rct_data()
  ) +
  geom_bar(position = "dodge", color = "black") +   
  facet_grid(CNT ~ ., scales = "free_y") + 
  scale_x_discrete(name = rct_labels()[["x"]]) +  
  scale_y_continuous(name = "number of students") +
  scale_fill_brewer(type = "seq", name = rct_labels()[["fill"]]) 
})
```
